---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  error = FALSE
)
```

# GKS2022

<!-- badges: start -->
<!-- badges: end -->

## Introduction

The code in this document is kept to a minimum. All the logic is implemented in functions. I only cover high-level functions.

## Setup

Make sure to install missing packages with `install.packages("missing-package")`. This package is not on CRAN so it must be installed from Github with the following command:

```{r}
# remotes::install_github("DavidBarke/GKS_2022")
```

```{r setup}
library(GKS2022)
library(ggplot2)
library(tibble)
library(pracma)
library(cli)
```

## Parameters

The function `ghaderi_params()` can be used to set the parameter values of the model. It outputs a list that can be passed to most of the other functions. The default values for the parameters are the ones used by @Ghaderi_2022.

```{r}
str(ghaderi_params())
```

## Fixed-point iteration

The function `fixed_point_iteration_pc` can be used to perform the (incorrect) fixed-point iteration for the wealth consumption ratio. The following code chunk outlines its logic.

```{r}
n <- 10 # Number of grid points
K <- 20 # Number of iterations

# Create a grid for lambda and pi
lambda <- linspace(log(0.005), log(11), n)
lambda <- exp(lambda)
pi <- linspace(0, 1, n)

pc_k <- pc_k1 <- ones(length(pi), length(lambda))

pc <- function(lambda_t, pi_t) {
  interp2(lambda, pi, pc_k, lambda_t, pi_t)
}

for (k in 1:K) { # loop over iterations
  for (i in 1:n) { # loop over lambda
    for (j in 1:n) { # loop over pi
      # j, i is not a mistake. interp2 expects pc_current in pi x lambda format
      # pc_t computes the right-hand side of equation 8
      pc_k1[j,i] <- pc_t(pc, lambda[i], pi[j])
    }
  }
  pc_k <- pc_k1
  cli_alert_info("Iteration {k}: avg. value: {1/n^2 * sum(pc_k)}")
}
```

As you can see the average wealth-consumption ratio increases with every iteration which is undesirable. The difference between subsequent iterations gets smaller but @Ghaderi_2022 suggest that the true average value should be around $1/3$.

## Figure 2: Learning Dynamics, Intensity Process, Consumption Growth

I replicate figure 2. First, I set the state variable $s_{t}$

```{r}
s_t <- rep(c(0, 1, 0), times = c(15, 70, 35))
```

Among other things, the function `simulation()` simulates the intensity process $\lambda_t$, belief evolution $\pi_t$, aggregate consumption growth process $\Delta c_t$, and price of a dividend claim $P_{d,t}$.

```{r}
sim <- simulation(s_t, pc_grid, pd_grid)

str(sim)
```

```{r, echo=FALSE}
ggplot(sim$data) + 
  geom_line(aes(x = t, y = s_t), color = "blue") +
  geom_line(aes(x = t, y = pi_t), color = "orange", linetype = "dashed") +
  theme_bw() +
  labs(
    title = "Panel A",
    x = "Months",
    y = "s_t, pi_t"
  ) +
  scale_x_continuous(
    expand = c(0, 0)
  )

ggplot(sim$data) +
  geom_line(aes(x = t, y = lambda_t), color = "black") +
  theme_bw() +
  labs(
    title = "Panel B",
    x = "Months",
    y = "lambda_t"
  ) +
  scale_x_continuous(
    expand = c(0, 0)
  )

ann_data <- tibble(
  t = 0:10,
  y = c(1, annual_growth(exp(sim$data$delta_c_t)))
)
ggplot(ann_data) +
  geom_line(aes(x = t, y = y), color = "black") +
  theme_bw() +
  labs(
    title = "Panel C",
    x = "Years",
    y = "C_{t+1} / C_t"
  ) +
  scale_x_continuous(
    expand = c(0, 0)
  )
```

The price of the dividend claim is obviously wrong.

```{r}
ggplot(sim$data) +
  geom_line(aes(x = t, y = P_D_t), color = "black") +
  theme_bw() +
  labs(
    title = "Panel D",
    x = "Months",
    y = "P_d,t"
  ) +
  scale_x_continuous(
    expand = c(0, 0)
  )
```

# Asset Pricing Moments

I would have liked to reproduce the simulations they did but without a correct price-dividend ratio this is a pointless endeavor. 

